Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-05-29 draft/paper1_jenny.tex
Edit M/L measurement

        \item \textbf{The \mstar{} within the inner 10 kpc} 
            (hereafter noted \minn{}). 
            According to the two-phase scenario, the ``in-situ'' star-formation 
            quickly builds up the inner, dense core of massive ETGs.  
            Based on recent observation (e.g.~\citealt{vanDokkum2010}) and 
            simulations (e.g. \citealt{RodriguezGomez2016}), the in-situ component
            dominates the \mstar{} within one effective radius ($R_{\mathrm{e}}$, 
            or 5-10 kpc) of $z{\sim}0$ massive ETGs.
            We therefore use \minn{} as proxy for the mass forged during the 
            ``in-situ'' phase. 
            Given the quality of the HSC data, we can reliably measure \minn{} over 
            our redshift range ($1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc 
            at redshift 0.3 and 0.5).  
            It is worth noting that, at very high-\mstar{} end, there can be 
            significant contribution of accreted stars within 10 kpc 
            (e.g. \citealt{RodriguezGomez2016). 
            We will further discuss the justification of this assumption in 
            \ref{ssec:twophase}.

@@

    To convert luminosities into stellar mass, we assume that these massive galaxies 
    can be well described by an average \m2l{}. 
    This is a reasonable assumption considering that they are mostly dominated by 
    old stellar populations and are known to have shallow color gradients. 
    We will further justify this point by measuring their median color profiles in 
    Section \ref{ssec:ell_color}.

@@

    In this work, we derive average \m2l{} using the Flexible Stellar Population 
    Synthesis\footnote{http://scholar.harvard.edu/cconroy/sps-models}
    (FSPS; \texttt{v2.4}; \citealt{FSPS}, \citealt{Conroy2010}) model based on the 
    MILES\footnote{http://www.iac.es/proyecto/miles/pages/stellar-libraries}
    (\citealt{MILES1}, \citealt{MILES2}) stellar library and assuming a
    \citet{Chabrier2003} IMF between 0.1 to 100 \msun. 
    The star formation history (SFH) is assumed to follow a delayed-$\tau$ model with 
    stochastic star bursts (see Appendix~\ref{app:sed}). 
    This SFH is appropriate for massive galaxies at low redshifts 
    (e.g.\ \citealt{Kauffmann2003}). 
    \update{
    For stellar metallicity 
    ($[\mathrm{M}/\mathrm{H}]=\log\ \mathrm{Z}/\mathrm{Z}_{\odot}$), we assume a flat 
    distribution between 0.004 to 0.03 (the highest value allowed by FSPS).
    } 
    We adopt the \citet{Calzetti2000} extinction law with a order two Gamma 
    distribution of $A_{V}$ between 0 to 2 magnitude. 
    A majority of our galaxies are red and quiescent and our results are 
    not very sensitive to parameters related to the SFH or the internal dust extinction. 
    To achieve reasonable sampling across these parameters, we generate 250000 models.

    We construct five band SEDs using the forced-photometry \cmodel{} magnitudes 
    corrected for Galactic extinction. 
    \cmodel{} only accounts for the statistical error on the flux measurement but does
    not account for systematic uncertainties in the model-fitting process. 
    It therefore underestimates the flux errors of bright galaxies. 
    For this work, we supply \texttt{iSEDFit} with simplified flux errors assuming 
    $S/N = 100$ for the $riz$ bands, and $S/N = 80$ for the $g$- and $y$-band 
    (on average, images in $gy$ bands are shallower in depth and/or have higher 
    background noise).  
    Although thse are still conservative estimates of the systematic uncertainties 
    involved in the model-fitting, tests using synthetic galaxies show that \cmodel{}
    provides excellent measurements of five-band colors, which are crucial for reliable
    \m2l{} estimates.
    The typical uncertainty of \logms{} is around 0.06-0.08 dex at \logms${\sim} 11.5$. 
    Please see Appendix~\ref{app:sed} for further details.

>>>>

        \item \textbf{The \mstar{} within the inner 10 kpc} 
            (hereafter noted \minn{}). 
            According to the two-phase scenario, the ``in-situ'' star-formation 
            quickly builds up the inner, dense core of massive ETGs.  
            Based on recent observation (e.g.~\citealt{vanDokkum2010}) and 
            simulations (e.g. \citealt{RodriguezGomez2016}), the in-situ component
            dominates the \mstar{} within one effective radius ($R_{\mathrm{e}}$, 
            or 5-10 kpc) of $z{\sim}0$ massive ETGs.
            We therefore use \minn{} as proxy for the mass forged during the 
            ``in-situ'' phase. 
            Given the quality of the HSC data, we can reliably measure \minn{} over 
            our redshift range ($1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc 
            at redshift 0.3 and 0.5).  
            It is worth noting that, at very high-\mstar{} end, there can be 
            significant contribution of accreted stars within 10 kpc 
            (e.g. \citealt{RodriguezGomez2016}). 
            We will further discuss the justification of this assumption in 
            \ref{ssec:twophase}.

@@

    To convert luminosities into \mstar{}, we assume that these massive galaxies 
    can be well described by an average \m2l{}. 
    This is a reasonable assumption considering that they are mostly dominated by 
    old stellar populations and are known to have only shallow color gradients. 
    We will further justify this point by measuring their median color profiles in 
    Section \ref{ssec:ell_color}.

@@

    In this work, we derive average \m2l{} using the Flexible Stellar Population 
    Synthesis\footnote{http://scholar.harvard.edu/cconroy/sps-models}
    (FSPS; \texttt{v2.4}; \citealt{FSPS}, \citealt{Conroy2010}) model based on the 
    MILES\footnote{http://www.iac.es/proyecto/miles/pages/stellar-libraries}
    (\citealt{MILES1}, \citealt{MILES2}) stellar library and assuming a
    \citet{Chabrier2003} IMF between 0.1 to 100 \msun. 
    The star formation history (SFH) is assumed to follow a delayed-$\tau$ model with 
    stochastic star bursts (see Appendix~\ref{app:sed}). 
    This SFH is appropriate for massive galaxies at low redshifts 
    (e.g.\ \citealt{Kauffmann2003}). 
    For stellar metallicity 
    ($[\mathrm{M}/\mathrm{H}]=\log\ \mathrm{Z}/\mathrm{Z}_{\odot}$), we assume a flat 
    distribution between 0.004 to 0.03 (the highest value allowed by FSPS).
    We adopt the \citet{Calzetti2000} extinction law with a order two Gamma 
    distribution of $A_{V}$ between 0 to 2 magnitude. 
    The majority of our galaxies are red and quiescent ones so the results are not 
    very sensitive to parameters related to the SFH or the internal dust extinction. 
    To achieve reasonable sampling across these parameters, we generate 250000 models.

    We construct five band SEDs using the forced-photometry \cmodel{} magnitudes 
    corrected for Galactic extinction. 
    \cmodel{} only accounts for the statistical error on the flux measurement but 
    does not account for systematic uncertainties in the model-fitting process. 
    It therefore underestimates the flux errors of bright galaxies. 
    For this work, we supply \texttt{iSEDFit} with simplified flux errors assuming 
    $S/N = 100$ for the $riz$ bands, and $S/N = 80$ for the $g$ and $y$ band 
    (on average, images in $gy$ bands are shallower in depth and/or have higher 
    background noise).  
    Although these are still conservative estimates of the systematic uncertainties 
    involved in the model-fitting, tests using synthetic galaxies show that \cmodel{}
    provides excellent measurements of five-band colors, which are crucial for 
    reliable \m2l{} estimates.
    The typical uncertainty of \logms{} is around 0.06-0.08 dex at \logms${\sim} 11.5$. 
    Please see Appendix~\ref{app:sed} for further details.
